Clustering in a hyperbolic model of complex networks.

### 2019-02-17 introduction.tex
typos

Our second result in on the clustering function for constant $k$.

@@

In particular, Theorem~\ref{thm:mainktoinfty} implies that
\[
	\frac{c(k_n; G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L^1} 1,
\]
so that the clustering function if the KPKVB model scales as $\gamma(k)$ as $k$ grows.

>>>>

Our second result is on the clustering function for constant $k$.

@@

In particular, Theorem~\ref{thm:mainktoinfty} implies that
\[
	\frac{c(k_n; G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L^1} 1,
\]
so that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows.

### 2019-02-17 paper.tex
typos

Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that $c(k)$, the average clustering over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. Our results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should scale with $k^{-1}$ as we let $k$ grow. We find that this is true only when $\alpha > \frac34$, while $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\alpha < \frac34$ and $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac34$.
\end{abstract}

>>>>

Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. Our results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should scale with $k^{-1}$ as we let $k$ grow. We find that this is true only when $\alpha > \frac34$, while $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\alpha < \frac34$ and $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac34$.
\end{abstract}

### 2019-02-17 proof_overview_finite_k.tex
typos

For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V} := \mathcal{P} \cap \Rcal$ and edges set such that
\[
	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
\]
where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$. 
Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting 
identified, which in particular 
%excludes boundary effects and 
makes the model invariant under horizontal shifts and reflections in vertical lines. 
The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some addition edges caused by 
the identification of the boundaries.

@@

\noindent
This can be reprased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and

>>>>

For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V} := \mathcal{P} \cap \Rcal$ and edges set such that
\[
	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
\]
where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$. 
Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting 
identified, which in particular 
%excludes boundary effects and 
makes the model invariant under horizontal shifts and reflections in vertical lines. 
The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some additional edges caused by 
the identification of the boundaries.

@@

\noindent
This can be rephrased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and
